Landscape composition and beneficial insects

### 2020-05-27 manuscript/manuscript_outline.Rmd
Converted to PDF.
- Need to update refs and tables

---
title: "Landscape composition and beneficial insects"
author: "Sam Robinson, Paul Galpern, et al."
date: "Spring 2020"
bibliography: refs.bib
csl: ecology-letters.csl
output:
  bookdown::html_document2:
    pandoc_args: ["--include-after-body=manuscript_appendix.md"]
---

@@

#Adds ** around text (makes it bold in RMarkdown)
boldRMD <- function(x) paste0('**',x,'**')
#Inverse of above
unboldRMD <- function(x) gsub('\\**','',x)

@@

#Extract Pterostichus melanarius results
pmelRes <- summary(PteMelMod$mod3)
pmelLinTerms <- pmelRes$p.table %>% as.data.frame() %>% 
  rownames_to_column('loc') %>% 
  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
pmelSmTerms <- pmelRes$s.table %>% as.data.frame() %>% 
  rownames_to_column('Smoother') %>% 
  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold

#Extract Pardosa distincta results
pdisRes <- summary(ParDisMod$mod3)
pdisLinTerms <- pdisRes$p.table %>% as.data.frame() %>% 
  rownames_to_column('loc') %>% 
  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
pdisSmTerms <- pdisRes$s.table %>% as.data.frame() %>% 
  rownames_to_column('Smoother') %>% 
  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold

#Extract Phalangium opilio results
opilRes <- summary(OpilioMod$mod3)
opilLinTerms <- opilRes$p.table %>% as.data.frame() %>% 
  rownames_to_column('loc') %>% 
  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
opilSmTerms <- opilRes$s.table %>% as.data.frame() %>% 
  rownames_to_column('Smoother') %>% 
  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold

@@

* We used a system of pitfall traps installed at roadsides, field margins, wetlands, and in-field sites across southern Alberta in 2017 (_need a map here_)
  + Pitfall traps consisted of 582 mL Solo® cups buried up to the rim, partially filled with ethylene glycol
  + All traps had 2cm (?) chicken wire mounted over the rim to prevent small vertebrates from falling into the traps
  + Traps at roadsides were located 5m (?) from the roads, while traps at in-field sites were installed 20, 100, 200m (?) along a transect from the nearest non-crop feature (wetland, grassland, pivot)
  + Specimens were collected from the traps every 14 days (SD: 2.9), and were identified to species

* We used three species of predatory arthropods that were present at very high abundances in the traps
  + _Pterostichus melanarius_ is predatory introduced ground beetle that is a wide-ranging generalist [@carcamo1994, @larsen2003, @busch_Msc]
  + It is commonly found in untilled grasslands [@purtauf2005] and grassy field margins may act as larval habitat [@desender1988]
  + _Pardosa distincta_ is a species of wolf spider that is common across the Canadian prairies, and is commonly found in ungrazed pastures [@carcamo2014]
  + Finally, _Phallangium opilio_ is a widely-distributed harvestment from the order Opilio
  +

* We modeled arthropod activity density as a function of landscape composition using generalized additive models @wood2017
    + To account for different lengths of trap exposure, log-days since trap placement was used as a fixed effect with its slope held at 1 (``offset" variable)
    + All models were fit using a negative binomial distribution
    + We fit our functional regression models using _mgcv_ version 1.8-31

* To characterize landscape composition surrounding the traps, we used classified landscape data from @AAFC_data
  + AAFC cropland landscape classifications are very accurate for cultivated fields (~90%), but are less accurate for non-crop areas (~70%)
  + We extracted the landscape composition within a circle of a fixed radius surrounding each trap location 
  + However, the radius of the circle necessary to characterize the landscape depends on the ``grain" of the landscape that is relevant to the abundance of a given organism (@addicott1987)
  + Therefore, we divided the landscape into annuli (rings) surrounding each trap location.
  + Each annulus was 30 m thick, and had inner radii ranging from 30 to 1470m, in increments of 30m.

  + Using functional regression [@ramsay2004], we were able to incorporate landscape information at different distance, allowing us to assess the impact of both local and regional landscape composition

@@

* We used functional regression to model the effect of landscape composition on activity density 
  +  Scalar-on-function (SoF) regression is a special type of functional linear regression model ($\hat{y}=X\beta$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$ (e.g. biomass in a plot (scalar) as a function of monthly average temperatures (vector)), and the values of the coefficients ($\beta$) are modeled as a smooth function $f(x)$ of the predictors
  + In our case, each column represents the proportion of a given landscape cover class within each annulus, with increasing radii away from the location of the trap, and the coefficients are a smooth function of distance ($\beta_i = f(distance_i)$), meaning that the coefficients represent the (additive) effect of a given type of landscape cover and  from the trap 
  + This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages [@addicott1987, @lima1996]
  + This technique has been used by other authors [@yen2014, @galpern2020]

@@

```{r PteMelCoefs-linTerms, echo=FALSE, warning=FALSE}
kable(pmelLinTerms,caption='\\label{tab:PteMelCoefs-linTerms} Linear terms for _Pterostichus melanarius_.',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
        digits=c(1,2,2,2,2),align='rrrrl')
```

```{r PteMelCoefs-smoothTerms, echo=FALSE, warning=FALSE}
kable(pmelSmTerms[c(1,2,4,5)],caption='\\label{tab:PteMelCoefs-smoothTerms} Smooth terms for _Pterostichus melanarius_, with effective degrees of freedom, Chi-squared coefficient, and p-value. _s_ indicates a thin-plate spline, _ti_ indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits. **NAMES OF SMOOTHING TERMS ARE CONFUSING - SHOULD BE SIMPLIFIED**',col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
        digits=c(1,2,2,2),align='rrll')
```

@@

* _Pardosa distincta_ activity density was also strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisCoefs-linTerms), \@ref(tab:ParDisCoefs-smoothTerms)), similar to _P. melanarius_.
  + However, _P. distincta_ had far lower activity density in canola than any other cover type (Figure \@ref(fig:ParDisCoefs-fixeff)a).
  + Interestingly, nearby canola appeared to act as a source of _P. distincta_ for surrounding landscape features, as activity density was positively related to the nearby proportion of canola (p = `r with(pdisSmTerms,unboldRMD(p[Smoother=='s(distMat):Canola']))`), at least early in the season (p = `r with(pdisSmTerms,unboldRMD(p[Smoother=='s(endDayMat):Canola']))`)
  + Pulse crops had a similar effect, acting as a source of _P. distincta_ early in the season, and acting as a mild sink later in the season (p = `r with(pdisSmTerms,unboldRMD(p[Smoother=='ti(distMat,endDayMat):Pulses']))`, Figure \@ref(fig:ParDisCoefs-fixeff)d)
  + Grassland acted as a weak source, at least earlier on in the season (p = `r with(pdisSmTerms,unboldRMD(p[Smoother=='s(endDayMat):Grassland']))`), and urban cover acted as a weak sink at intermediate distances (~600m)
  + Similar to _P. melanarius_, _P. distincta_ activity density had a very strong temporal and spatial component (both p = `r with(pdisSmTerms,unboldRMD(p[grepl('E,N',Smoother)]))`, Figure \@ref(fig:ParDisCoefs-raneff))

```{r ParDisCoefs-linTerms, echo=FALSE, warning=FALSE}
kable(pdisLinTerms,caption='\\label{tab:ParDisCoefs-linTerms} Linear terms for _Pardosa distincta_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
        digits=c(1,2,2,2,2),align='rrrrl')
```

```{r ParDisCoefs-smoothTerms, echo=FALSE, warning=FALSE}
kable(pdisSmTerms[c(1,2,4,5)],caption='\\label{tab:ParDisCoefs-smoothTerms} Smooth terms for _Pardosa distincta_, with effective degrees of freedom, Chi-squared coefficient, and p-value. _s_ indicates a thin-plate spline, _ti_ indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
        digits=c(1,2,2,2),align='rrll')
```

@@

@@

* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, unboldRMD(p[loc=='Pivot']))`, `r with(opilLinTerms, unboldRMD(p[loc=='Wetland']))`)  
  + However, unlike _P. melanarius_ or _P. pardosa_, _P. opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,unboldRMD(p[Smoother=='ti(distMat,endDayMat):Pasture']))`)
  + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`,`r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
  + The temporal and spatial components, as in the other two species, were very strong (both p = `r with(opilSmTerms,unboldRMD(p[grepl('E,N',Smoother)]))`, and Easting

```{r OpilioCoefs-linTerms, echo=FALSE, warning=FALSE}
kable(opilLinTerms,caption='\\label{tab:OpilioCoefs-linTerms} Linear terms for _Phalangium opilio_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
        digits=c(1,2,2,2,2),align='rrrrl')
```

```{r OpilioCoefs-smoothTerms, echo=FALSE, warning=FALSE}

kable(opilSmTerms[c(1,2,4,5)],caption='\\label{tab:OpilioCoefs-smoothTerms} Smooth terms for _Phalangium opilio_, with effective degrees of freedom, Chi-squared coefficient, and p-value. _s_ indicates a thin-plate spline, _ti_ indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
        digits=c(1,2,2,2),align='rrll')
```

@@

>>>>

---
title: Landscape composition and beneficial insects
subtitle: I like carabids
author:
  - name: Samuel Robinson
    email: samuel.robinson@ucalgary.ca
    affiliation: University of Calgary
    footnote: 1
  - name: Paul Galpern
    email: paul.galpern@ucalgary.ca
    affiliation: University of Calgary
address:
  - code: University of Calgary
    address: 2500 University Drive NW, Calgary, AB, Canada
footnote:
  - code: 1
    text: "Corresponding Author"
date: "Spring 2020"
abstract: Ground-dwelling arthropods are important generalist predators in prairie agro-ecosystems. However, we don't know what types of landscape features they live in. Some may act as sources of arthropods during some parts of the year, and sinks during others. We examined 3 widely-distributed species of arthropods, and used functional regression to examine their habitat preferences. We found that trees/shrubs, and roadside grasses acted as sources of arthropods. Other features did not function as significant sources or sinks. Farmers should keep these landscape intact in order to preserve populations of generalist predators to defend their crops.

bibliography: refs.bib
csl: ecology-letters.csl
output: 
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
    toc: false
    fig_caption: false
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}

---

<!-- This argument in YAML header adds "manuscript_appendix.md" after document -->
<!-- output: -->
<!--   bookdown::html_document2: -->
<!--     pandoc_args: ["--include-after-body=manuscript_appendix.md"] -->

@@

boldRMD <- function(x) paste0('**',x,'**') #Makes text bold in rMarkdown
boldLaTeX <- function(x) paste0('\\textbf{',x,'}') #Makes text bold in LaTeX

@@

#Extract Pterostichus melanarius results
pmelRes <- summary(PteMelMod$mod3)
pmelLinTerms <- pmelRes$p.table %>% as.data.frame() %>% 
  rownames_to_column('loc') %>% 
  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
pmelSmTerms <- pmelRes$s.table %>% as.data.frame() %>% 
  rownames_to_column('Smoother') %>% 
  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold

#Extract Pardosa distincta results
pdisRes <- summary(ParDisMod$mod3)
pdisLinTerms <- pdisRes$p.table %>% as.data.frame() %>% 
  rownames_to_column('loc') %>% 
  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
pdisSmTerms <- pdisRes$s.table %>% as.data.frame() %>% 
  rownames_to_column('Smoother') %>% 
  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold

#Extract Phalangium opilio results
opilRes <- summary(OpilioMod$mod3)
opilLinTerms <- opilRes$p.table %>% as.data.frame() %>% 
  rownames_to_column('loc') %>% 
  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
opilSmTerms <- opilRes$s.table %>% as.data.frame() %>% 
  rownames_to_column('Smoother') %>% 
  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold

@@

* We used a system of pitfall traps installed at roadsides, field margins, wetlands, and in-field sites across southern Alberta in 2017 (_need a map here_)
  + Pitfall traps consisted of 582 mL Solo® cups buried up to the rim, partially filled with ethylene glycol
  + All traps had 2cm chicken wire mounted over the rim to prevent small vertebrates from falling into the traps
  + Traps at roadsides were located 5m from the roads, while traps at in-field sites were installed 20, 100, 200m (?) along a transect from the nearest non-crop feature (wetland, grassland, pivot)
  + Specimens were collected from the traps every 14 days (SD: 2.9), and were identified to species

* We used three species of predatory arthropods that were present at very high abundances in the traps
  + _Pterostichus melanarius_ is predatory introduced ground beetle that is a wide-ranging generalist [@carcamo1994, @larsen2003, @busch_Msc]
  + It is commonly found in untilled grasslands [@purtauf2005] and grassy field margins may act as larval habitat [@desender1988]
  + _Pardosa distincta_ is a species of wolf spider that is common across the Canadian prairies, and is commonly found in ungrazed pastures [@carcamo2014]
  + Finally, _Phallangium opilio_ is a widely-distributed harvestmen from the order Opilio

* We modeled arthropod activity density as a function of landscape composition using generalized additive models @wood2017
    + To account for different lengths of trap exposure, log-days since trap placement was used as a fixed effect with its slope held at 1 (``offset" variable)
    + All models were fit using a negative binomial distribution
    + We fit our functional regression models using _mgcv_ version `r packageVersion('mgcv')`

* To characterize landscape composition surrounding the traps, we used classified landscape data from @AAFC_data
  + AAFC cropland landscape classifications are very accurate for cultivated fields (~90%), but are less accurate for non-crop areas (~70%)
  + We extracted the landscape composition within a circle of a fixed radius surrounding each trap location 
  + However, the radius of the circle necessary to characterize the landscape depends on the ``grain" of the landscape that is relevant to the abundance of a given organism [@addicott1987]
  + Therefore, we divided the landscape into annuli (rings) surrounding each trap location.
  + Each annulus was 30 m thick, and had inner radii ranging from 30 to 1470m, in increments of 30m.
  + Using functional regression [@ramsay2004], we were able to incorporate landscape information at different distance, allowing us to assess the impact of both local and regional landscape composition

@@

* We used functional regression to model the effect of landscape composition on activity density 
  +  Scalar-on-function (SoF) regression is a special type of functional linear regression model ($\hat{y}=X\beta$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$ (e.g. biomass in a plot (scalar) as a function of monthly average temperatures (vector)), and the values of the coefficients ($\beta$) are modeled as a smooth function $f(x)$ of the predictors
  + In our case, each column represents the proportion of a given landscape cover class within each annulus, with increasing radii away from the location of the trap, and the coefficients are a smooth function of distance ($\beta_i = f(distance_i)$), meaning that the coefficients represent the (additive) effect of a given type of landscape cover and  from the trap 
  + This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages [@addicott1987 @lima1996]
  + This technique has been used by other authors [@yen2014, @galpern2020]

@@

```{r PteMelCoefs-linTerms, echo=FALSE, warning=FALSE}
pmelLinTerms %>% select(-p) %>% 
  kable(.,caption='Linear terms for \\emph{Pterostichus melanarius}',
      col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
      digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
```

```{r PteMelCoefs-smoothTerms, echo=FALSE, warning=FALSE}

pmelSmTerms %>% select(-Ref.df,-p) %>% 
  kable(.,caption='Smooth terms for \\emph{Pterostichus melanarius}. \\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',
      col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
      digits=c(1,2,2,2),align='rrll',escape=TRUE)
```

@@

* _Pardosa distincta_ activity density was also strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisCoefs-linTerms), \@ref(tab:ParDisCoefs-smoothTerms)), similar to _P. melanarius_.
  + However, _P. distincta_ had far lower activity density in canola than any other cover type (Figure \@ref(fig:ParDisCoefs-fixeff)a).
  + Interestingly, nearby canola appeared to act as a source of _P. distincta_ for surrounding landscape features, as activity density was positively related to the nearby proportion of canola (p = `r with(pdisSmTerms,pTable[Smoother=='s(distMat):Canola'])`), at least early in the season (p = `r with(pdisSmTerms,pTable[Smoother=='s(endDayMat):Canola'])`)
  + Pulse crops had a similar effect, acting as a source of _P. distincta_ early in the season, and acting as a mild sink later in the season (p = `r with(pdisSmTerms,pTable[Smoother=='ti(distMat,endDayMat):Pulses'])`, Figure \@ref(fig:ParDisCoefs-fixeff)d)
  + Grassland acted as a weak source, at least earlier on in the season (p = `r with(pdisSmTerms,pTable[Smoother=='s(endDayMat):Grassland'])`), and urban cover acted as a weak sink at intermediate distances (~600m)
  + Similar to _P. melanarius_, _P. distincta_ activity density had a very strong temporal and spatial component (both p = `r with(pdisSmTerms,pTable[grepl('E,N',Smoother)])`, Figure \@ref(fig:ParDisCoefs-raneff))

```{r ParDisCoefs-linTerms, echo=FALSE, warning=FALSE}
pdisLinTerms %>% select(-p) %>% 
  kable(.,caption='\\label{tab:ParDisCoefs-linTerms} Linear terms for _Pardosa distincta_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
        digits=c(1,2,2,2,2),align='rrrrl')
```

```{r ParDisCoefs-smoothTerms, echo=FALSE, warning=FALSE}
pdisSmTerms %>% select(-Ref.df,-p) %>% 
  kable(.,caption='Smooth terms for \\emph{Pardosa distincta}. \\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',
        col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
        digits=c(1,2,2,2),align='rrll',escape=TRUE)
```

@@

## _Pardosa moesta_

```{r ParMoeCoefs-linTerms, echo=FALSE, warning=FALSE}
pdisLinTerms %>% select(-p) %>% 
  kable(.,caption='\\label{tab:ParMoeCoefs-linTerms} Linear terms for _Pardosa moesta_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
        digits=c(1,2,2,2,2),align='rrrrl')
```

```{r ParMoeCoefs-smoothTerms, echo=FALSE, warning=FALSE}
pdisSmTerms %>% select(-Ref.df,-p) %>% 
  kable(.,caption='\\label{tab:ParMoeCoefs-smoothTerms} Smooth terms for _Pardosa moesta_. \\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',
        col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
        digits=c(1,2,2,2),align='rrll')
```

```{r ParMoeCoefs-fixeff, echo=FALSE, fig.cap='\\label{fig:ParMoeCoefs-fixeff} Landscape influence on _Pardosa moesta_ activity density. Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE). Dashed line on panels b-f represents zero effect. Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}  
  include_graphics('../figures/Pardosa_moesta_fixeff.png')
```

```{r ParMoeCoefs-raneff, echo=FALSE, fig.cap='\\label{fig:ParMoeCoefs-raneff} Temporal and spatial components of _Pardosa moesta_ activity density'}
  include_graphics('../figures/Pardosa_moesta_raneff.png')
```

@@

* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, pTable[loc=='Pivot'])`, `r with(opilLinTerms, pTable[loc=='Wetland'])`)  
  + However, unlike _P. melanarius_ or _P. pardosa_, _P. opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,pTable[Smoother=='ti(distMat,endDayMat):Pasture'])`)
  + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`,`r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
  + The temporal and spatial components, as in the other two species, were very strong (both p = `r with(opilSmTerms,pTable[grepl('E,N',Smoother)])`, and Easting

```{r OpilioCoefs-linTerms, echo=FALSE, warning=FALSE}
opilLinTerms %>% select(-p) %>% 
  kable(.,caption='Linear terms for \\emph{Phalangium opilio}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
        digits=c(1,2,2,2,2),align='rrrrl')
```

```{r OpilioCoefs-smoothTerms, echo=FALSE, warning=FALSE}
opilSmTerms %>% select(-Ref.df,-p) %>% 
  kable(.,caption='\\label{tab:OpilioCoefs-smoothTerms} Smooth terms for \\emph{Phalangium opilio}. \\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction. All terms except for day and (E,N) are functional regression fits.',
        col.names=c('Smoothing term','Eff. df_','$\\chi^2$','p'),
        digits=c(1,2,2,2),align='rrll')
```

@@

\newpage

# Supplementary Material {-}

\beginsupplement
